---
title: "Group 37 CA Pollution Burden"
author: "Tommy King & German Silva"
date: "11/13/2021"
output: html_document
---

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# installing necessary packages
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
# Reading in the data 
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r}
ggplot(data = ces, aes(x= white_percent, y = ces_3_0_score))+
  geom_hex() + 
  labs(x = "% of White Population", 
       y = "CalEnviroScreen pollution score", 
       caption = "Figure 1: White Population Pollution Burden Score: 
       Negative Correlation between percentage of white population and 
       pollution burdens within these communities. Namely, the higher amount 
       of white people within a commuity, the less likely it is for that 
       community to be affected by hazardous pollution, determined by the
       CalEnviroScreen Pollutoin Burden test to analyze marginalized 
       communities and the environmental injustices they have received 
       due to inequitable pollution.") +
  ggtitle("White Population Pollution Burden Score")+
  scale_fill_gradient(low = "grey", high = "darkred") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0), plot.title = element_text(hjust = 0.5))
```

As shown in Figure 1, there is a general downhill trend between the percent of the population that is White and the CalEnviroScreen pollution burden score meaning that on average as the percentage of the population that is White increases the pollution burden score decreases. 

Data Sources:

California Office of Environmental Health Hazard Assessment. (2018). "CalEnviroScreen 3.0",         California Environmental Protection Agency.

United States Census Bureau. (2010). California census data, www.census.gov